Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-19 LatexNotes/Notes.tex
NM

Little remark for the very careful reader: the plot in Fig. \ref{match_theta} is out of date (used $\Lambda=16$) and is not consistent with Figs.~\ref{matchH} and \ref{match_micro} (which used $\Lambda = 8$).

@@

>>>>

@@

\np
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Big-time results}

Now lets do some more serious runs with larger $\Lambda$. The major challenge is that the acceptance rate plummets as $\Lambda$ grows, meaning that we either have to take many more samples or develop a smarter strategy. For now, we will do the first. To run more samples, I had to modify the organization of the code. I am still exploiting the ability to precompute a list of $H_3$ and $H_2$ values, but I cannot precompute and store the entire list at once because it will not fit in memory. So instead, I take several sweeps each with a manageable number of samples (usually about $10^7$).

Figure \ref{Lambda16Run} shows a run with $\Lambda = 16$, with $10^7$ samples per sweep and 200 sweeps for a total of $2 \times 10^9$ nominal samples. The main parameter to vary is the upstream inverse temperature $\theta^-$. More negative $\theta^-$ gives a more significantly skewed distribution of $u$, but also results in noisier statistics due to the lower acceptance rate. I therefore chose $\theta^- = -0.2$ since it gives a good balance of the two. The top panel of the figure shows $\theta^+$ as a function of $\theta^-$ and the histograms for $\theta^- = -0.2$. The bottom panel shows microstate information, including the pdf of displacement, $u$, and the spectrum. Notice the definite skew of the downstream displacement and the decay of both upstream and downstream spectra. For this run, the upstream acceptance rate was $1\%$ and the downstream rate was $0.08\%$.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.95 \textwidth]{Lambda16Run}
\caption{Big run with $\Lambda = 16$ and $2 \times 10^9$ nominal samples.}
\label{Lambda16Run}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
